---
title: "QMM LP Assignment2"
author: "Jyoti Phogat"
date: "2022-10-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#The Weigelt Corporation has three branch plants with excess production capacity. Fortunately, the cor-poration has a new product ready to begin production, and all three plants have this capability,so some of the excess capacity can be used in this way. This product can be made in three sizes–large, medium,and small–that yield a net unit profit of $420, $360, and $300, respectively.Plants 1, 2, and 3 have the excess capacity to produce 750, 900, and 450 units per day of this #product, respectively, regardless of the size or combination of sizes involved.


#The amount of available in-process storage space also imposes a limitation on the production rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000 square feet, respectively, of in-process storage space available for a day’s production of this product. Each unit of the large, #medium, and small sizes produced per day requires 20, 15, and 12 square feet, respectively. Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large, medium, and small #sizes, respectively, would be sold per day.

#At each plant, some employees will need to be laid off unless most of the plant’s excess production capacity can be used to produce the new product. To avoid layoffs if possible, management has decided that the plants should use the same percentage of their excess capacity to produce the new product. #Management wishes to know how much of each of the sizes should be produced by each of the plants to maximize profit.

#a. Define the decision variables

#The decision variables are the number of units of the new product, regardless its size, that should be produced on each plant to maximize the company’s profit.

#Note:

#Xi = means the number of units produced on each plant, where i= 1 (Plant 1), 2 (Plant 2), and 3 (Plant3)

#L, M, and S = means the product’s size, where L = large, M = medium, and S = small.

#The decision variables are:

#XiL = number of large items produced on plant i, where i= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).
#XiM = number of medium items produced on plant i, where i= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).
#XiS = number of small items produced on plant i, where i= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).


#b. Formulate a linear programming model for this problem.

#Let
#XiL = number of large items produced on plant i, where i= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).
#XiM = number of medium items produced on plant i, where i= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).
#XiS = number of small items produced on on plant i, where i= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).


#Maximize profit

#Z = 420 (X1L + X2L + X3L) + 360 (X1M + X2M + X3M) + 300 (X1S + X2S + X3S)


#Constraints:

#Total number of size’s units produced regardless the plant:
#L = X1L + X2L + X3L
#M = X1M + X2M + X3M
#S = X1S + X2S + X3S #Production capacity per unit by plant each day:
#Plant 1 = X1L + X1M + X1S 750
#Plant 2 = X2L + X2M + X2S 900
#Plant 3 = X3L + X3M + X3S 450 

#Storage capacity per unit by plant each day: 
#Plant 1 = 20X1L +15X1M + 12X1S 13000
#Plant 2 = 20X2L + 15X2M + 12X2S 12000
#Plant 3 = 20X3L + 15X3M + 12X3S 5000

#Sales forecast per day:

#L = X1L + X2L + X3L 900
#M = X1M + X2M + X3M 1200
#S = X1S+X2S+X3S 750 

#The plants should use the same percentage of their excess capacity to produce the new product.

#X1L + X1M + X1S/750 = X2L + X2M + X2S/900 = X3L + X3M + X3S/450


#—————SOLUTION USING R—————————

```{r}
install.packages("knitr") 
library(knitr) 
install.packages("tinytex") 
tinytex::install_tinytex(force=TRUE) 
```

# Import the lpSolve package.

```{r}
install.packages("lpSolve")
library(lpSolve)
```
# Setting coefficients of the objective function assignment_objfunc
```{r}
assignment_objfunc <- c(420, 420, 420,
360, 360, 360,
300, 300, 300)
```

# Setting the left hand side of the problem's constraints as assignment_leftconst

```{r}
assignment_leftconst <- matrix(c(1, 1, 1, 0, 0, 0, 0, 0, 0,
0, 0, 0, 1, 1, 1, 0 ,0, 0,
0, 0, 0, 0, 0, 0, 1, 1, 1,
20, 15, 12, 0, 0, 0, 0, 0, 0,
0, 0, 0, 20, 15, 12, 0, 0, 0,
0, 0, 0, 0, 0, 0, 20, 15, 12,
1, 0, 0, 1, 0, 0, 1, 0, 0,
0, 1, 0, 0, 1, 0, 0, 1, 0,
0, 0, 1, 0, 0, 1, 0, 0, 1,
900, 900, 900, -750, -750, -750, 0, 0, 0,
0, 0, 0, 450, 450, 450, -900, -900, -900,
450, 450, 450, 0, 0, 0, -750, -750, -750), nrow = 12, byrow = TRUE)
```

# Setting the right hand side of the problem's constraints as assignment_rightconst

```{r}
assignment_rightconst <- c(750,
900,
450,
13000,
12000,
5000,
900,
1200,
750,
0,
0,
0)
```

# Setting the unequality signs as assignment_uneqsigns

```{r}
assignment_uneqsigns <- c("<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"=",
"=",
"=")
```

# Set up the final lp problem

```{r}
lp("max", assignment_objfunc, assignment_leftconst, assignment_uneqsigns, assignment_rightconst)
```

# To get the solution of the lp problem

```{r}
lp("max", assignment_objfunc, assignment_leftconst, assignment_uneqsigns, assignment_rightconst)$solution
```
